---
title: "CookingConversion"
author: "Itzel Zapata-Oropesa"
date: "5/1/2022"
output: html_document
---
[Github](https://github.com/ItzelZapata-Oropesa/FinalProject_CreatingAPackage)

## 'Cooking Conversion' package

This package that hs been created contains various functions that convert
cooking measurments amoungst themselves.

```{r}
#Load library
library(cookingConversions)

```

Below we will use different functions created with in this package:

```{r , echo=TRUE}
#Use the function to find out how many cups are in 5 gallons

gals2cups(5)

#After viewing this function we can see that there are 80 cups in 5 gallons
```

Below we will use more functions to find somemore conversions

```{r, echo=TRUE}
#How many tablespoons are in four cups
cups2Tbsp(4)

#After finding out how many tablespoons are in four cups, use a different 
#to figure out how many teaspoons are in four cups
Tbsp2tsp(64)

```
Creating a dataframe to use for our functions


```{r}
ingredient <- c("butter", "whiteSugar", "lightBrownSugar", "vanillaExtract", 
                "Eggs", "allPurposeFlour", "bakingSoda", "bakingPowder", "chocoChips")
measurments <- c(1, 1, 1, 2, 2, 3, 1, 1/2, 2)
cookies<- data.frame(ingredient, measurments)
cookies$units <- c("NA", "cup", "cup", "tsp", "NA", "cups", "tsp", "tsp", "cups")

#view head of dataframe
head(cookies)

```
Using functions on new dataframe

```{r}
#Figuring out how many tablespoons of milk we need to make cookies
cups2Tbsp(cookies$measurments[2])

#Repeating the same process but with AP flour
cups2Tbsp(cookies$measurments[6])
```

  ##Inside my function
Taking a closer look at the inside of my functions
note: all my functions created for this package follow the same format
```{r}
Tbsp2tsp <- function(x){
  teasp <- 1
  Tbsp <- 3 * teasp
  z <- x * Tbsp
  y <- "teaspoons"
  return(c(z,y))
}
```

Above we can see that to begin I set a teaspoon equal to one. The based on prior
knowledge I know 3 teaspoons are equal to one tablesppon. Therefore I create a 
variable named Tbsp that is set to be 3 time a teaspoon (which in this case is
1). Next I create a variable names Z which I set the input value to be
multiplied by Tbsp. Lastly I create a variable names Y which I input a text
string which is the name of the variable we are solving for. My last step is
to set the function to return both the Z and Y variable to display our results.
